Lessons learned from bugs in models of human history

### 2020-05-22 paper.tex
Fix typo

\begin{figure}[ht]
\begin{center}
\makebox[\textwidth][c]{\includegraphics{figures/prs_fig.pdf}}
\caption{\textbf{The transferability of PRS under neutrality}.
    \textbf{(A)} In~\citet{martin2017human}, the simulated demographic model did not apply demographic
    events in the past, so continental populations were simulated as isolated with low levels of migration
    for all time. The correct model has historical events as shown in Fig.~\ref{fig:ooa_stats}A.
    \textbf{(B-G)} We repeated the simulation experiment in~\cite{martin2017human} using the correct
    demographic model.
    GWAS summary statistics were computed from 10,000 case and control subjects in the European
    population, and the distribution of inferred PRS were compared across the three simulated populations.
    Unlike the original study, we do not observe large differences in mean inferred PRS across
    the three populations (C, D), and while risk prediction in the African and East Asian population is
    still reduced compared to the European population, the reduction in prediction accuracy is not as
    large as reported in the original study (E-G).
    Correlations between true and inferred polygenic scores were computed over 100 simulation replicates.
    For direct comparison to the original study, see Figure~5 in~\citet{martin2017human}.
}
\label{fig:prs}
\end{center}
\end{figure}

>>>>

\begin{figure}[ht]
\begin{center}
\makebox[\textwidth][c]{\includegraphics{figures/prs_fig.pdf}}
\caption{\textbf{The transferability of PRS under neutrality}.
    \textbf{(A)} In~\citet{martin2017human}, the simulated demographic model did not apply demographic
    events in the past, so continental populations were simulated as isolated with low levels of migration
    for all time. The correct model has historical events as shown in Fig.~\ref{fig:ooa_stats}A.
    \textbf{(B-G)} We repeated the simulation experiment in~\cite{martin2017human} using the correct
    demographic model.
    GWAS summary statistics were computed from 10,000 case and control subjects in the European
    population, and the distribution of inferred PRS were compared across the three simulated populations.
    Unlike the original study, we do not observe large differences in mean inferred PRS across
    the three populations (C, D), and while risk prediction in the African and East Asian populations is
    still reduced compared to the European population, the reduction in prediction accuracy is not as
    large as reported in the original study (E-G).
    Correlations between true and inferred polygenic scores were computed over 100 simulation replicates.
    For direct comparison to the original study, see Figure~5 in~\citet{martin2017human}.
}
\label{fig:prs}
\end{center}
\end{figure}
